\maketitle

The following \emph{moving sofa problem} was first proposed to the literature by Leo Moser in 1966 \cite{moser1966problem}.
\begin{problem}[Moving Sofa Problem \cite{romik2018differential}]
A \emph{sofa} is any planar shape that can be moved around a right-angled corner in a hallway of unit width. What is the maximum area of a sofa? 
\end{problem} 
Since then, the problem gained a reasonable attention from the mathematics community over more than 50 years \cite{gerver1992moving,  romik2018differential, kallus2018improved}. However, the full problem remains unsolved to this date.

In 1997, Gerver \cite{gerver1992moving} constructed a sofa of area $2.2195\dots$ with considerations of local optimality. He then conjectured that his sofa attains the maximum area possible, which still holds the current record till this date.
The sofa's boundary consists of 3 line segments and 15 analytic curves, making it even complicated to just describe the shape.
This renders the problem as an infinite-dimensional, non-convex optimization problem with conjecturally a rather artificial and complicated optimum.

The goal of this project is to prove that the Gerver's sofa indeed attains the maximum possible area of a sofa.
The main strategy to successfully control the area function $\cA \colon \cS \ra \RR$ on the space of all sofas $\cS$ is \emph{bootstrapping} the upper bound $\cA_i$ of $\cA$. 
We successively develop more refined upper bounds $\cA_i$ of $\cA$ which are easier to control, as we also narrow down the scope $\cS_i \subset \cS$ of sofas that contains a maximum sofa.
From a possibly crude upper bound $\cA_i$ of area $\cA$, we obtain that a maximal sofa should be in the set $\cS_i = \{\cA_i \geq 2.2195\dots \}$. 
Using particular properties of $\cA_i$ and $\cS_i$, we develop an upper bound $\cA_{i+1}$ that is more closer to $\cA$ than from $\cA_i$. 
This also refines the possible scope $\cS_{i + 1} = \{\cA_{i + 1} \geq 2.2195\dots \}$ from $\cS_i$, which allows to further develop more refined bounds and regions.

\textcolor{blue}{Note that the following plan has not been executed fully at this moment.}

Due to the complicated and somewhat artificial nature of the optimum, computer assistance is involved in different steps of the bootstrapping process. 
In the first step, a C++ program is developed to estimate the area of sofas from above with polygonal area $\cA_0$.
The program then proves an important lemma for the set $\cS_0$, which enables us to produce a much refined upper bound $\cA_1$ which is both continuous and convex.
Symbolic calculations then produce certificates satisfying Karush–Kuhn–Tucker (KKT) conditions to show linear inequalities satisfied by $\cS_1$. 
This allows us then stratify $\cS_1$ into smaller pieces $\cS_{2, \varphi, \varphi'}$ parametrized by real values $\varphi, \varphi'$ with a convex upper bound $\cA_{2, \varphi, \varphi'}$. The values $\varphi, \varphi'$ corresponds to the moments where a hypothetical sofa starts/stops touching the inner corner of a sofa.
We then finally obtain the optimum value $R_{\varphi, \varphi'}$ of $\cA_{2, \varphi, \varphi'}$ for each $(\varphi, \varphi')$ by solving convex programming with KKT certificates.
Numeric/symbolic calculations are then used to show that $R_{2, \varphi, \varphi'}$ is maximized exactly when the sofa is the Gerver's sofa, where the value of $R_{2, \varphi, \varphi'}$ matches with the actual area $2.2195\cdots$, completing the proof.

We are currently in the stage of producing a full computer-assisted proof. 
Because the proof depends much on computer results, we plan to formalize our proof with collaborative effort in future. 
We expect the formalization task to challenge and thus develop multiple aspects of formal proof technology:
\begin{itemize}
	\item Proper formalization of area bounded by a non-self-intersecting curve.
	\item Formalizing the whole search tree of a branch-and-bound case analysis proof with backtracking algorithm.\footnote{Relevant discussions are made in \url{https://leanprover-community.github.io/archive/stream/113488-general/topic/Verifying.20backtracking.20algorithms.html} }
	\item Formalization of existence/inequalities on real values satisfying certain formula. e.g.) existence of a unique $x$ that minimizes $\sin(x) / x$ for $2 \leq x \leq 6$.
	\item Formalization of symbolic calculations.
\end{itemize}

\input{setup}

\input{monotone}

\input{injectivity}

\input{concaveub}

\input{future}