\section{Monotone Sofas}

In this section, we build up the notion of \emph{monotone sofas}, a special subcollection $\cS_0$ of sofas with additional structure on its shape and movement.
In terms of geometry, a monotone sofa $S$ consists of its \emph{cap} $\cC(S)$, a convex set of a particular shape, subtracted by the sofa's \emph{niche} $\cN(S)$, an uncountable union of triangles.
In terms of movement, a monotone sofa always rotates clockwise while touching the outer sides $a$ and $c$ of the hallway $L$.
We prove that any sofa of maximum area is contained in a monotone sofa, so that it is sufficient to maximize the area of a monotone sofa. 
It turns out that the collection $\cS_0$ of monotone sofas can be embedded as a closed, convex subset of an affine space $\cT_0$.
This way, we will later be able to maximize or solve for concave quadratic functional $\cA_1 \colon \cT_0 \ra \RR$, which is an upper bound of the actual area functional $\cA \colon \cS \ra \RR$.

\textcolor{red}{Add figure here, and likely an animation that describes the concept briefly}

\subsection{Monotone Movement}
By Lemma \ref{lem:rot-angle}, we can restrict our attention to sofas that rotate by an angle of $\beta \in [0, \pi / 2]$.
Such an arbitrary sofa $S$ can be moved in the following way we name as a \emph{monotone movement}.
First, move a copy of $S_0$ inside $L$ in the positive $x$ and $y$ direction until it hits both sides $a$ and $c$ of the hallway $L$.
Then, for every moment $t \in [0, \beta]$, we rotate the sofa by the unit angular speed while keeping it touching the sides $a$ and $c$.
This way, the sofa $S_t$ is parametrized by the angle it is rotated during movement.
Such a movement is used by previous works \cite{gerver1992moving, romik2018differential, kallus2018improved}.
The rest of this subsection defines the monotone movement and justifies that it is a valid movement.

\textcolor{blue}{[An animation of arbitrary movement, compared to a monotone movement will be great]}

First we introduce some definitions before describing the monotone movement.
We will use the following unit vectors to describe the geometry of a general sofa.
\begin{definition}
For any $t \in \RR$, let $u_t$ be the vector $(\cos t, \sin t)$ and $v_t$ be the vector $(\sin t, -\cos t)$ so that $u_t, v_t$ forms the frame rotated counterclockwise by an angle of $t$.
\end{definition}
In particular, we define the support functions $p_S, q_S$ of a sofa $S$ as the following.
\begin{definition}
\label{def:support}
For any $t \in \RR$ and a closed, compact set $S \subset \RR^2$, define the support functions $p_S, q_S \colon \RR \ra \RR$ as
$$p_S(t) = \max_{x \in S} x \cdot u_t$$
and
$$q_S(t) = \max_{x \in S} x \cdot v_t.$$
Note that $q_S(t) = p_S(t + \pi / 2)$ is just the shift of $p_S$ by $\pi / 2$.
Also, both $p_S$ and $q_S$ can be considered as real-valued functions on $\RR / 2 \pi \RR$.
If the sofa $S$ is clear from the context, we omit the subscript and denote the support functions as $p$ and $q$.
\end{definition}
\begin{theorem}
\label{thm:support-continuous}
For any closed, compact $S \subset \RR^2$, the support functions $p_S$ and $q_S$ are continuous.
\end{theorem}
\begin{proof}
(omitted)
\end{proof}

We will use the following `basic' polygons often as well. 
\begin{definition}
\label{def:polygons}
Define the \emph{quadrants} $Q^+ = (-\infty, 1] \times (-\infty, 1]$ and $Q^- = (-\infty, 0) \times (-\infty, 0)$.
With this, the hallway $L$ can be expressed as $Q^+ \setminus Q^-$.
Also, define the \emph{half-planes} $R_H = \RR \times [0, \infty)$ and $R_V = [0, \infty) \times \RR$.

For any angle $\beta \in [0, \pi / 2]$, define the set $P_\beta = H \cap \Rot_\beta(V)$. The set $P$ is a parallelogram for $\beta < \pi / 2$, and is the horizontal strip $P = H$ for $\beta = \pi / 2$.
We will omit the subscript $\beta$ when it is clear from the context, and call such $P$ a \emph{parallelogram} no matter whether $\beta = \pi / 2$ or not.
Likewise, define the \emph{fan} $F_\beta = R_H \cap \Rot_\beta(R_V)$, for which we will also omit the subscript if possible.
\end{definition}

Now we show that any sofa with rotation angle in between $0$ and $\pi / 2$ can be repositioned to have the following \emph{monotone movement}.
\begin{definition}
\label{def:monotone-movement}
A sofa $(S, f_t)$ with hallway movement $g_t = f_t^{-1}$ and rotation angle $\beta \in [0, \pi / 2]$ is said to have a \emph{monotone movement} if it satisfies the following.
\begin{itemize}
	\item The sofa movement $f_t$ is parametrized by angles $t \in [0, \beta]$.
	\item $q_{S}(0) = p_{S}(\beta) = 1$. That is, $S$ touches the sides $c(0) = g_0(c)$ and $a(\beta) = g_\beta(a)$ of $L_0$ and $L_\beta$ respectively.
	\item $g_{t} = \Rot_t \circ T_{(p_{S}(t) -1, q_{S}(t) -1)}$. That is, the hallway $L_{t} = g_t(L)$ at time $t$ is $L$ rotated counterclockwise by an angle of $t$ and translated to touch $S$ on the sides $a(t)$ and $c(t)$.
\end{itemize}
\end{definition}

\begin{theorem}
\label{thm:monotone-movement}
Let $(S', f'_t)$ be any sofa with shape $S'$, movement $f'_t$ and a rotation angle of $\beta \in [0, \pi / 2]$.
Then we can reposition $S'$ to a sofa shape $S$ (that is, there is an orientation-preserving isometry $m$ so that $S = m(S')$) with sofa movement $f_t$ and hallway movement $g_t = f_t^{-1}$ parametrized by $t \in [0, \beta]$ which is monotone (Definition \ref{def:monotone-movement}).
\end{theorem}
\begin{proof}
First we set up the shape $S$ of the new sofa.
Geometrically, $S$ is the translation of $S'_0$ that touches the upper and right sides of $P = H \cap R_\beta(V)$ inside.
Note that $P$ is a parallelogram with lower left corner $(0, 0)$ when $\beta \in [0, \pi / 2)$, and $P$ is the horizontal strip $H$ when $\beta = \pi / 2$.
The following paragraph is merely a formalization of this step.

Define $S$ as the translation of $S'_0 = f'_0(S')$ by a vector $v \in \RR^2$ that satisfies $q_{S}(0) = p_{S}(\beta) = 1$.
The condition for $v$ to satisfy $q_{S}(0) = p_{S}(\beta) = 1$ are the followings.
\begin{gather*}
	q_{S}(0) = q_{S'_0}(0) + v \cdot v_0 = 1\\
	p_{S}(\beta) = p_{S'_0}(\beta) + v \cdot u_\beta = 1
\end{gather*} 
These are linear conditions of $v$, and such a $v$ exists uniquely for every $\beta \in [0, \pi / 2)$ as $v_0$ and $u_\beta$ forms a basis of $\RR^2$.
For $\beta = \pi / 2$, the two equations overlap as $p_S(\pi / 2) = q_S(0)$ for any sofa $S$ by definition, so take any solution of $v$.
Now by letting $m = T_v \circ f'_0$ and sending the sofa $(S', f'_t)$ under $m$, we have a sofa of shape $S = m(S')$ and movement $\tilde{f}_t = f'_t \circ m^{-1}$, so that $\tilde{f}_t(S) = f'_t(S') = S'_t$. That is, the movement $\tilde{f}_t$ of $S$ parametrized by $t \in [0, T]$ follows the exact same movement of $S'$.
Also, we get $q_S(0) = p_S(\beta) = 1$ by how we chose $v$. 

Now we show that the sofa shape $S$ with movement $f_t = g_t^{-1}$ defined as $g_t = R_t \circ T_{(p_{S}(t) -1, q_{S}(t) -1)}$ over $t \in [0, \beta]$ gives a valid sofa.
First, observe that $f_t$ is continuously parametrized by $t$ because $p_S(t)$ and $q_S(t)$ are continuous (Theorem \ref{thm:support-continuous}).
It remains for us to show that 
\begin{itemize}
	\item $S$ is contained in $g_0(H)$
	\item $S$ is contained in $L_t = g_t(L)$ for all $t \in [0, \beta]$
	\item $S$ is contained in $g_\beta(V)$
\end{itemize}
by the moving hallway definition of a sofa (Definition \ref{def:moving-hallway}). 
First we show the second item $S \subseteq L_t$.

Before showing $S \subseteq L_t$, we observe the following. The initial map $\tilde{f}_0$ of the movement $\tilde{f}$ is
$T_{-v}$, a translation. 
So it has a rotation angle of $0$.
As $\tilde{f}_t$ has the same rotation angle $\beta$ as the original movement $f'_t$, the final map $\tilde{f}_T$ of the movement $\tilde{f}$ has a rotation angle of $\beta$.
Because the rotation angle of $\tilde{f}_{t'}$ is continuous respect to $t' \in [0, T]$,
by the intermediate value theorem, for every $\theta \in [0, \beta]$ we have
some $t' \in [0, T]$ such that $\tilde{f}_{t'}$ has a rotation angle of $\theta$.

Now we take arbitrary $t \in [0, \beta]$ and show $S \subseteq L_t$.
We can find some $t \in [0, T]$ such that $\tilde{f}_t$ has a rotation angle of $\theta$ by the previous paragraph.
So the moving hallway $\tilde{L} = \tilde{f}_t^{-1}(L)$ at time $t$ is rotated counterclockwise from $L$ by $t$.
Geometrically, $L_t$ is a copy of $\tilde{L}$ translated in the directions $-u_\theta$ and $-v_\theta$ until it hits the sofa $S$.
The following paragraph is a formal justification of this idea.

\textcolor{blue}{TODO: complete the argument here}
By the definition of $g_\theta$, we have $L_\theta$
. This completes the proof that $L_\theta$ contains $S$.
\end{proof}

\subsection{Monotone Sofas}

We observed in Theorem \ref{thm:monotone-movement} that any sofa $S$ with rotation angle in $[0, \pi / 2]$ can be repositioned to have a monotone movement $f_t$.
Equation \ref{eq:intersection} then tells us that $S$ is contained in the following intersection of rotated stripes and hallways.
\begin{definition}
\label{def:monotonization}
For any sofa $S$ with rotation angle $\beta \in [0, \pi / 2]$ and monotone movement $f_t$, define the following set $M(S)$ as the \emph{monotonization} of sofa $(S, f_t)$.
\begin{equation}
\label{eq:monotone-sofa}
M(S) = H \cap \Rot_\beta(V) \cap \bigcap_{0 \leq t \leq \beta} L_t
\end{equation}
Here, we follow the notations of Definition \ref{def:moving-hallway}.
\end{definition}
We show that monotonization of any sofa with monotone movement is also a sofa.

\begin{theorem}
\label{thm:monotonization-connected}
Let $(S, f_t)$ be a sofa with monotone movement, so that it has a rotation angle $\beta \in [0, \pi / 2]$ and sofa (and hallway) movement of $f_t$ (and $g_t = f_t^{-1}$) respectively.
Denote the moving sofa as $S_t = f_t(S)$ and the moving hallway as $L_t = g_t(L)$.
Then the monotonization $M(S)$ contains $S$, and is itself a sofa with the same movement $f_t$.
\end{theorem}
\begin{proof}
The set $M(S)$ is closed by definition, and it is bounded as $H \cap R_\beta(V)$ is bounded for $\beta < 0$ and $H \cap L_{\pi / 4}$ is bounded for $\beta = \pi / 2$.
Also, the set $M(S)$ contains $S$ by Definition \ref{def:moving-hallway}.
So it suffices to show that $M(S)$ is connected.
Then, by Definition \ref{def:moving-hallway}, the movement $f_t$ is a valid movement of sofa shape $M(S)$ and $(M(S), f_t)$ is a sofa.

Fix an arbitrary point $v \in N(S)$.
We will show that there is a line segment inside $M(S)$ connecting $v$ to a point in $S$. This completes the proof of connectedness of $M(S)$, as $M(S)$ is the union of $S$ with line segments extending from $S$.

Let $l_\theta$ be the line through $v$ that makes an angle $\theta \in [\beta, \pi / 2]$ in counterclockwise direction from the $x$-axis. 
Regardless of $\theta$, the intersection $s_\theta = l_\theta \cap M(S)$ is either a line segment or an empty set. This is because $s_\theta$ is the intersection of $l_\theta \cap H$, $l_\theta \cap \Rot_\beta(V)$, and $l_\theta \cap L_t$ for all $t \in [0, \beta]$, all line segments contained in $l_\theta$.

\textcolor{blue}{TODO: 'Sanitize': add figures, but make sure that the argument does not appeal much to some hidden geometric assumption.}

Now it only remains to show that for some $\theta$, $l_\theta$ overlaps with $S$, so that the segment $s_\theta = l_\theta \cap M(S)$ connects $v$ with a point in $S$. 
If either one of $l_\beta$ or $l_{\pi / 2}$ overlaps with $S$, then we are done. 
Assume otherwise that none of $l_\beta$ and $l_{\pi / 2}$ overlaps with $S$.
Since $S$ is nonempty and connected, it is either on the left side of $l_{\pi / 2}$ or the right side of $l_{\pi / 2}$.
As we are working with the monotone movement of $S$, $S$ touches the side $a(0)$ of $L_0$ inside $L_0$. This implies that $S$ is on the right side of $l_{\pi / 2}$.
A similar argument with the side $c(\beta)$ of $L_\beta$ shows that $S$ is on the left side of $l_\beta$.
Now move $l_\theta$ continuously, taking $\theta$ from $\beta$ to $\pi / 2$. As $S$ is on the different sides of $l_\theta$ for $\theta = \beta$ and $\pi / 2$, at some point the line $l_\theta$ will pass through $S$. This completes the proof.
\end{proof}

With the following definition, monotonization is a process of (potentially) enlarging any sofa with monotone movement to a monotone sofa, while keeping the same movement.
\begin{definition}
Call a sofa \emph{monotone} if it is the monotonization $(M(S), f_t)$ of any sofa $(S, f_t)$ with rotation angle $\beta \in [0, \pi / 2]$ and monotone movement $f_t$.
\end{definition}
We will show that monotonization is a \emph{projection} from all sofas with monotone movement to monotone sofas.
That is, monotonization not only maps any sofa to a monotone sofa, but also fixes any monotone sofa.
In other words, $M(M(S)) = M(S)$.
To do that, we need to first analyze the geometry of monotone sofas.

Let $(S, f_t)$ be any sofa with monotone movement and rotation angle $\beta \in [0, \pi / 2]$.
We use Definition \ref{def:polygons} in the following discussion.
Rewriting $L_t$ as $Q^+_t \setminus Q^-_t$ where $Q^+_t = g_t(Q^+)$ and $Q^-_t = g_t(Q^-)$, we have the following equality on the monotone sofa $M(S)$. 
\begin{align}
M(S) & = H \cap R_\beta(V) \cap \bigcap_{0 \leq t \leq \beta} L_t \\
\label{eq:monotone-sofa-structure}
& = \left(P \cap \bigcap_{0 \leq t \leq \beta} Q^+_t \right) \setminus \bigcup_{0 \leq t \leq \beta} \left(F \cap Q^-_t \right) 
\end{align}
\begin{definition}
\label{def:cap-niche}
Let $(S, f_t)$ be any sofa with monotone movement and rotation angle $\beta \in [0, \pi / 2]$. Define the \emph{cap} of $S$ as
$$\cC(S) = P \cap \bigcap_{0 \leq t \leq \beta} Q^+_t$$
and the \emph{niche} of $S$ as
$$\cN(S) = \bigcup_{0 \leq t \leq \beta} \left(F \cap Q^-_t \right).$$
For each $t \in [0, \beta]$, let $T_t = F \cap Q^-_t$ be the \emph{wedge} of $S$ at angle $t$.
Consequently, $M(S) = \cC(S) \setminus \cN(S)$ and $\cN(S) = \cup_{0 \leq t \leq \beta} T_t$ by Equation \ref{eq:monotone-sofa-structure}.
\end{definition}

\begin{definition}
\label{def:boundary}
For each sofa $S$ with a monotone movement and a rotation angle $\beta \in [0, \pi / 2]$, let $I_\beta = [0, \beta] \cup [\pi / 2, \pi / 2 + \beta]$ be the set of \emph{fundamental angles} of $S$.

Let the \emph{boundary} $\partial \cC(S)$ of the cap $\cC(S)$ be the set of all points $x \in \cC(S)$ such that there is some $t \in [0, \beta]$ so that either $x \cdot u_t = p(t)$ or $x \cdot v_t = q(t)$.
\end{definition}

The cap of a sofa is a convex set.  
\begin{lemma}

\end{lemma}

\begin{theorem}
For any sofa 
\end{theorem}

\textcolor{blue}{TODO: this is not obvious. We need to develop sufficient language on convex sets and its boundary.}
It turns out that $\partial \cC(S)$ is a closed convex curve that looks like \textcolor{blue}{TODO: add some figure and description}

The `interesting set' for each $\beta \in [0, \pi/2]$ is 

\begin{theorem}
\label{thm:monotone-sofa-structure}
For any sofa $S$ with monotone movement $f_t$, the niche $\cN(S)$ is contained in $\cC(S) \setminus \partial \cC(S)$.
Also, the support functions of $S$ and $M(S)$ match. That is, $p_S = p_{M(S)}$ and $q_S = q_{M(S)}$.
\end{theorem}
\begin{proof}
\textcolor{red}{TODO: convert this old writing to current writeup}

Since we are working with the canonical movement of $S$, $a(t)$ and $c(t)$ for all $t \in [0, \beta]$ are tangent lines of $S$ from above. 
$a(t)$ forms an angle of $t$ from the $y$-axis, and $c(t)$ forms the angle of $t$ from the $x$-axis.
Consequently, $\cC$ is a bounded convex set with tangent lines $a(t)$ and $c(t)$ for all $0 \leq t \leq \beta$ from above and sides $b(\beta)$ and $d(0)$ from below.
Define $\partial \cC$ as the boundary segment of $\cC$ touched by lines $a(t)$ and $c(t)$ for all $0 \leq t \leq \beta$.
Then $\partial \cC$ is a continuous curve consisting of two convex segments, each with tangent lines $\{a(t)\}_{0 \leq t \leq \beta}$ and $\{c(t)\}_{0 \leq t \leq \beta}$ respectively, joined at the vertex $a(\beta) \cap c(0)$ of $P$ for $\beta < \pi / 2$ or the segment $\partial \cC \cap c(0)$ for $\beta = \pi / 2$. 
The endpoints of $\partial \cC$ are $E_{l} = c(\beta) \cap b(\beta)$ and $E_{r} = a(0) \cap d(0)$ .
This, with the theorem below, characterizes the shape of a normal sofa.

Let $\cF$ be the fan above the line $b(\beta)$ and $d(0)$ with vertex $O = b(\beta) \cap d(0)$.
We only need to show that $P \cap Q^-_t$ is contained in $\cC \setminus \partial \cC$ for all $0 < t < \beta$.
When $\xx(t)$, the corner of $Q_t^-$, is not in $\cF$, $P \cap Q^-_t$ is empty and we are done.

So assume $\xx(t) \in \cF$. There are three possible configurations of $Q_t^-$ in $\cF$. \textcolor{blue}{Figure here}.
In all three cases, we only need to show the followings for all :
\begin{enumerate}
	\item The point $F_l = d(t) \cap b(\beta)$ is on the strictly right side of the endpoint $E_l$ of $\partial \cC$ in $b(\beta)$.
	\item The point $F_r = b(t) \cap d(0)$ is on the strictly left side of the endpoint $E_r$ of $\partial \cC$ in $c(0)$.
	\item The point $\xx(t)$ is inside $\cC$.
\end{enumerate}
We first show that (1) holds.
Say that a point $p_0$ is further than $p_1$ in the direction of nonzero vector $v \in \RR^2$ if and only if $p_0 \cdot v > p_1 \cdot v$.
For a fixed $v$, this is a partial order. 
$c(t) \cap a(\beta)$ is further than $d(t) \cap b(\beta)$ in the direction of $v_\beta$ (they are the intersection points of boundary lines of strips $V_\beta$ and $f^{-1}_t(H)$).
Take any point $q$ in $\partial \cC$ with tangent line $c(t)$. 
$q$ is further than $c(t) \cap a(\beta)$ in the direction of $v_\beta$.
Finally, the endpoint $c(\beta) \cap b(\beta)$ is further than $q$ in the direction of $v_\beta$ as the arc from $q$ to $c(\beta) \cap b(\beta)$ in $\partial \cC$ is directed towards the positive direction of $v_\beta$.
In conclusion, $c(\beta) \cap b(\beta)$ is further than $d(t) \cap b(\beta)$ in the direction of $v_\beta$ and (1) is shown.
\textcolor{blue}{TODO: this needs pictures}

A symmetric argument can be applied to show (2).

Assume by contradiction that (3) is false. That is, $\xx(t)$ is outside $\cC$ for some $0 < t < \beta$.
By (1) and the angular monotonicity of $\partial \cC$, the line connecting $F_l$ and $\xx(t)$ only meets $\partial \cC$ at most one point.
Since $F_l$ is inside $\cC$ by (1) and $\xx(t)$ is outside $\cC$ the segment connecting $F_l$ and $\xx(t)$ meets $\partial \cC$ at exactly one point (*).
Likewise, the segment connecting $F_r$ and $\xx(t)$ meets $\partial \cC$ at exactly one point (**).
Let $P_l$ and $P_r$ be the points in $S$ touching $c(t)$ and $a(t)$ respectively. 
Then the connected component of $P_l$ and $P_r$ in $S$ are disjoint by (*) and (**), leading to contradiction (we want more rigor for this step).
\textcolor{blue}{TODO: this needs pictures}
\end{proof}

\begin{definition}
Any sofa $S$ with monotone movement $f_t$ is a \emph{monotone sofa} if $S$ is exactly same as the set $M(S)$ in Equation \ref{eq:monotone-sofa}.
\end{definition}
\begin{theorem}
Any sofa of rotation angle in $[0, \pi / 2]$ is, after some reposition by some orientation-preserving isometry, is contained in a monotone sofa.
\end{theorem}
\begin{proof}
Take any sofa $S$. After some reposition, $S$ admits a monotone movement $f_t$ by Theorem \ref{thm:monotone-movement}.
By Theorem \ref{thm:monotone-sofa-connected}, the shape $M(S)$ is also a sofa with the same movement $f_t$.
By Theorem \ref{thm:monotone-sofa-structure}, the support function of $S$ and $M(S)$ matches.
Now note that a monotone movement solely depends on the support function of the sofa's shape by definition.
So $f_t$ is not only the monotone movement of $S$, but also of $M(S)$.
Now $(M(S), f_t)$ is a sofa with monotone movement. Consequently, $M(M(S)) = M(S)$ and so $(M(S), f_t)$ is a monotone sofa. 
\end{proof}
Thus, it suffices to look for monotone sofas if we want to find a sofa of maximum area.

\subsection{Space of Monotone Sofas}
Monotone sofas form a convex, closed subset of a Banach space for a fixed rotation angle $\beta \in [0, \pi / 2]$.

\textcolor{red}{The following stub will be used to write a more clear description}

\subsection{Differential Geometry of a Monotone Sofa}
\textcolor{red}{Under construction. The following text comes from previous writings and needs to undergo major changes.}

Now we describe the differential geometry of a normal sofa and its canonical movement.
The main argument will exploit the properties throughly.

We first define the `discrete' variants of the vertices of a normal sofa $S$ on its boundary $\partial \cC$. This will be used later to bound geometric values of $S$.
\begin{definition}
Fix an arbitrary normal sofa $S$ with rotational angle $\beta$ and angles $t_1, t_2 \in [0, \beta]$ different from each other. We define the followings:

$A_{t_1, t_2}$ is the intersection of line $a(t_1)$ and $a(t_2)$.
$C_{t_1, t_2}$ is the intersection of line $c(t_1)$ and $c(t_2)$.
$g_{t_1, t_2}$ is the signed distance between points $A_{t_1, t_2}$ and $\mathbf{y}(t_1)$ on the line $a(t_1)$.
The value is positive when $\yy(t_1)$ is above $A_{t_1, t_2}$. 
$h_{t_1, t_2}$ is the signed distance between points $C_{t_1, t_2}$ and $\mathbf{y}(t_1)$ on the line $c(t_1)$.
The value is positive when $\yy(t_1)$ is above $C_{t_1, t_2}$.
\end{definition}

\begin{proposition}
\label{prop:disc-leg-len}
For any $t$ and $t_1 < t_2$ such that $t_1$ and $t_2$ are different from $t$,
$A_{t, t_1}$ and $A_{t, t_2}$ are both on the line $a_{t}$ and $A_{t, t_2}$ is closer to $\yy(t)$ than $A_{t, t_1}$. 
Consequently, $g_{t, t_1} > g_{t, t_2}$.
Likewise, $C_{t, t_1}$ and $C_{t, t_2}$ are both on the line $c_{t}$ and $C_{t, t_1}$ is closer to $\yy(t)$ than $C_{t, t_2}$. 
Consequently, $h_{t, t_1} < h_{t, t_2}$.
\end{proposition}

Now we define the continuous vertices of the boundary $\partial \cC$.

\begin{definition}
\label{def:cont-leg-len}
For a normal sofa $S$, define 
$$
A^+_{t}= \lim_{t' \rightarrow t^+} A_{t, t'} \quad
A^-_{t}= \lim_{t' \rightarrow t^-} A_{t, t'} \quad
C^+_{t}= \lim_{t' \rightarrow t^+} C_{t, t'} \quad
C^-_{t}= \lim_{t' \rightarrow t^-} C_{t, t'}.
$$
With this, $A^+_{t}$ and $C^+_{t}$ are defined for all $t \in [0, \beta)$.
Let $C^+_\beta = c(\beta) \cap b(\beta)$.
Likewise, $A^-_{t}$ and $C^-_{t}$ are defined for all $t \in (0, \beta]$.
Let $A^-_0 = d(0) \cap a(0)$.

Let 
\begin{itemize}
\item $g^+_t$ be the distance between $A^+_t$ and $\mathbf{y}(t)$,
\item $g^-_t$ be the distance between $A^-_t$ and $\mathbf{y}(t)$,
\item $h^+_t$ be the distance between $C^+_t$ and $\mathbf{y}(t)$,
\item $h^-_t$ be the distance between $C^-_t$ and $\mathbf{y}(t)$.
\end{itemize}
In other words, 
$$
g^+_{t}= \lim_{t' \rightarrow t^+} g_{t, t'} \quad
g^-_{t}= \lim_{t' \rightarrow t^-} g_{t, t'} \quad
h^+_{t}= \lim_{t' \rightarrow t^+} h_{t, t'} \quad
h^-_{t}= \lim_{t' \rightarrow t^-} h_{t, t'}
$$
for appropriate values of $t$.
\end{definition}

The line segment connecting $A_{t}^-$ and $A_{t}^+$ is the edge of $\mathcal{C}$ touching $a(t)$. Consequently $g_t^- \geq g_t^+$.
Likewise, the line segment connecting $C_{t}^-$ and $C_{t}^+$ is the edge of $\mathcal{C}$ touching $c(t)$. Consequently $h_t^- \leq h_t^+$.

The lengths $g_t^\pm$ and $h_t^\pm$ of the `legs' extending from $\yy(t)$ to $A_t^\pm$ and $C_t^\pm$ respectively are important as they determine the velocity of the inner corner $\xx(t)$.

\begin{definition}
For any sofa $S$, $\mathbf{v}^+ (t)$ is the right derivative of $\mathbf{x}$ at $t$ and $\mathbf{v}^- (t)$ is the left derivative of $\mathbf{x}$ at $t$. That is,
$$
\mathbf{v}^{-} (t_0) = \lim_{t \rightarrow t_0^-} \frac{\mathbf{x}(t) - \mathbf{x}(t_0)}{t - t_0} \qquad
\mathbf{v}^{+} (t_0) = \lim_{t \rightarrow t_0^+} \frac{\mathbf{x}(t) - \mathbf{x}(t_0)}{t - t_0}.
$$
\end{definition}

\begin{lemma}
\label{lem:leg}
For any normal sofa $S$, $\mathbf{v}^+ (t)$ exists for any $0 \leq t < \pi / 2$ and is equal to the following. 
\begin{align*}
	\vv^+(t) = -(g_t^+ - 1) \cdot u_t + (h^+_t - 1) \cdot v_t
\end{align*}

Likewise, $\mathbf{v}^- (t)$ exists for all $0 < t \leq \pi / 2$ and is equal to the following.
\begin{equation*}
	\vv^-(t) = -(g^-_t - 1) \cdot u_t + (h^-_t - 1) \cdot v_t
\end{equation*}
\end{lemma}

\begin{proof} (sketch)
Take any $0 \leq t < \pi / 2$ and set $s = t + \delta$ for sufficiently small and arbitrary $\delta > 0$. We simplify $\vv^+(t) = \lim_{\delta \rightarrow 0^+}(\mathbf{x}(s) - \mathbf{x}(t)) / \delta$.
	
Since $A_{t, s}$ is on lines $a(t)$ and $a(s)$, it satisfies both 
	$$A_{t, s} \cdot u_t = \mathbf{x}(t) \cdot u_t + 1$$ 
and 
	$$A_{t, s} \cdot u_s = \mathbf{x}(s) \cdot u_s + 1.$$
		
	Rewrite $u_s = \cos \delta \cdot u_t + \sin \delta \cdot v_t$ on the second equation and we have
	\begin{align*}
		A_{t, s} \cos \delta \cdot u_t + A_{t, s} \sin \delta \cdot v_t =  	\cos \delta (\mathbf{x}(s) \cdot u_t) + \sin \delta (\mathbf{x}(s) \cdot v_t) + 1.
	\end{align*}
	
	Group by $\cos \delta$ and $\sin \delta$ and substitute $A_{t, s} \cdot u_t$ with first equation then
	$$ \cos \delta (\mathbf{x}(s) \cdot u_t - \mathbf{x}(t) \cdot u_t) + (1 - \cos \delta)
	= \sin \delta (A_{t, s}  (s) \cdot v_t - \mathbf{x}(s) \cdot v_t) .
	$$
	
	Divide by $\delta$ and send $\delta$ to zero. We get
	$$ \mathbf{v}^+(t) \cdot u_t  = (A^+(t) - \mathbf{x}(t)) \cdot v_t$$
	
	Note that $g_t^+ = (\mathbf{y}(t) - A^+(t)) \cdot v_t = (\mathbf{x}(t) - A^+(t))\cdot v_t + 1$ so
	we have 
	$$ \mathbf{v}^+(t) \cdot u_t = 1 - g_t ^+.$$
	
	A similar argument can be applied to show $\vv^+(t) \cdot v_t = h_t^+ - 1$ and thus the first equation of the theorem. 
	A symmetric argument shows the second equation of the theorem.
\end{proof}
